MCC Kids Model Predictions

### 2019-03-08 papers/full_paper/methods.Rmd
advance model description for paper

#          id = subid)%>%

@@

#   select(experiment,id,age_bin,age_num,trial,condition,agent,correct)

@@

#          id =subid)%>%
#   select(experiment,id,age_bin,age_num,trial,correct)

@@

#          alignment = Alignment)%>%

@@

#   select(experiment, id,age_bin,age_num,trial, speaker, alignment, agent, correct_inf)

@@

# children ex1
child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
# children ex2 preference
child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
# children ex3
child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
```

>>>>

#          minage = min(age_num))%>%

@@

#   select(experiment,id,age_bin,age_num,minage,trial,condition,agent,correct)

@@

#          id =subid,
#          minage = min(age_num))%>%
#   select(experiment,id,age_bin,age_num,minage,trial,correct)

@@

#          alignment = Alignment,
#          minage = min(age_num))%>%

@@

#   select(experiment, id,age_bin,age_num,minage,trial, speaker, alignment, agent, correct_inf)

@@

# children ex1
child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
# children ex2 preference
child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
# children ex3
child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv")

# model predictions adults ex3
ex3_model_predictions <- readRDS("../../stats/saves/ex3_model_predictions.rds")
# model comparison adults ex3
ex3_model_comparison <- readRDS("../../stats/saves/ex3_model_comparison.rds")
# model predictions adults ex4
ex4_model_predictions <- readRDS("../../stats/saves/ex4_model_predictions.rds")
# model comparison adults ex4
ex4_model_comparison <- readRDS("../../stats/saves/ex4_model_comparison.rds")
```

### 2019-03-08 papers/full_paper/models.Rmd
advance model description for paper

## Model utensils code

@@

@@

## Pragmatic RSA model code

@@

## Adult models

### Experiment 3
#### Model parameters and data

```{r ex3 data}
# load data  from experiment 4 to infer noise parameter
adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv") 
```

@@

#### Model predictions

@@

@@

ggplot(data = ex_3_cor_plot,aes(x = mean, y = data_mean, col = "#BB5566")) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = 1)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  guides(col = F)+
  facet_grid ( ~ model) +
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
  theme_few()

@@

#### Model comparison

@@

ex3_model_comparison <- bind_rows(
  ex3_pragm_model_loglike,
  ex3_prior_only_model_loglike,
  ex3_flat_prior_model_loglike
)%>%
  mutate(model = reorder(model,logP))
```
##### Plot for likelihoods

@@

### Experiment 4

#### Model parameters and data
```{r ex4 data}
# load data  from experiment 4 to infer noise parameter
adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv") 
```

```{r}
# load data from prior strength manipulation experiments to set priors

adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
```

@@

@@

ggplot(data = ex_4_cor_plot,aes(x = mean, y = data_mean, col = prior_manipulation)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = 1)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = 1)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid ( ~ model) +
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
  theme_few(base_size = ) + 
  scale_colour_ptol()
```

#### Model comparison

@@

ex4_model_comparison <- bind_rows(
  ex4_pragm_model_loglike,
  ex4_prior_only_model_loglike,
  ex4_flat_prior_model_loglike
)%>%
  mutate(model = reorder(model,logP))
```

@@

>>>>

# Model code

## Model utensils

@@

var prior_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "circle", id:1, location: 2}
]

@@

var addNoise = function(dist, noiseParam){
   Infer({model: function(){ 
      return flip(noiseParam) ? uniformDraw([0, 1]) : sample(dist)
    }
   })
}

var foreach = function(fn, lst) {
    var foreach_ = function(i) {
        if (i < lst.length) {
            fn(lst[i]);
            foreach_(i + 1);
        }
    };
    foreach_(0);
};

var logistic = function(x) {1 / (1 + Math.exp(-x))}

var levels = function(df, label){
  return _.uniq(_.map(df, label));
}

## RSA model code

@@

## Experiment 3

### Model parameters and data

```{r ex3 data}
# load data from experiment 3
adult_ex3_data <-read_csv(file="../../stats/data/adult_ex3.csv") 
```

@@

### Model predictions

@@

#saveRDS(ex_3_pred, "../../stats/saves/ex3_model_predictions.rds")

@@

ggplot(data = ex_3_cor_plot,aes(x = mean, y = data_mean, col = "#BB5566")) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  guides(col = F)+
  facet_grid ( ~ model) +
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
  theme_few()

@@

### Model comparison

@@

ex3_model_comparison <- bind_rows(
  ex3_pragm_model_loglike,
  ex3_prior_only_model_loglike,
  ex3_flat_prior_model_loglike
)%>%
  mutate(model = reorder(model,logP))

#saveRDS(ex3_model_comparison, "../../stats/saves/ex3_model_comparison.rds")

```
##### Plot for likelihoods

@@

## Experiment 4

### Model parameters and data
```{r ex4 data}
# load data  from experiment 4 
adult_ex4_data <-read_csv(file="../../stats/data/adult_ex4.csv") 
```

```{r}
# load data from prior strength manipulation experiments to set priors
adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
```

@@

#saveRDS(ex_4_pred, "../../stats/saves/ex4_model_predictions.rds")

@@

ggplot(data = ex_4_cor_plot,aes(x = mean, y = data_mean, col = prior_manipulation)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 0.7, size = 0.5)+
  geom_point(size = 2)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .7)+
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0,size = .7)+
  coord_fixed()+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid ( ~ model) +
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mean, y = data_mean), inherit.aes = F, size = 3)+
  theme_few(base_size = ) + 
  scale_colour_ptol()
```

### Model comparison

@@

ex4_model_comparison <- bind_rows(
  ex4_pragm_model_loglike,
  ex4_prior_only_model_loglike,
  ex4_flat_prior_model_loglike
)%>%
  mutate(model = reorder(model,logP))

#saveRDS(ex4_model_comparison, "../../stats/saves/ex4_model_comparison.rds")
```

@@

## RSA model code
```{r rsa model}

childRsaModel <- '
var literalListener = cache(function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
})

var speaker = cache(function(obj, lexiconName, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance, priorProbs);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
})

var pragmaticListener = cache(function(utterance, priorProbs, speakerOptimality){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs, speakerOptimality);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
})

## Model parameters and data

```{r ex3 data}
# children ex3 data
child_ex3_data <-read_csv(file="../../stats/data/child_ex3.csv") 
```

```{r}
# load data from ex1 manipulation experiments to set speaker optimality parameter
child_ex1_data <-read_csv(file="../../stats/data/child_ex1.csv")
# load data from ex2 experiment to set priors
child_ex2_data <-read_csv(file="../../stats/data/child_ex2.csv") 
```

```{r}
childModelParam <- '
var prefData = dataFromR.prefData
var infData = dataFromR.infData

var all_conditions = levels(prefData, "condition")

  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})

  foreach(function(row){

  var age = row.age_num
  var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)

    var inf_priorProbs = [.5, .5, .5]

  var rsaPredictions = pragmaticListener({label: "dax", point: 2 },
   inf_priorProbs, speakerOptimality) 
   observe(rsaPredictions, row.correct)

  }, infData)

  var pref_params = map(function(cndtn){

    var conditionData = _.filter(prefData, {condition: cndtn})

    var pref_slope = uniformDrift({a: -2, b: 2, width: 0.4})
    var pref_int = uniformDrift({a: -2, b: 2, width: 0.4})

    foreach(function(row){

      var age = row.age_num

      var priorReg = logistic(pref_int + pref_slope * (age - row.minage))
      var priorProbs= [1-priorReg, priorReg]

      var priorPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: prior_objects, ps: priorProbs}));
      return obj.shape == "circle" ? 1 : 0
      }})

      observe(priorPredictions, row.correct)

    }, conditionData)

    return [
      {param: "pref_int", val: pref_int, condition: cndtn}, 
      {param: "pref_slope", val: pref_slope, condition: cndtn}
    ]

  }, all_conditions)

  return _.flatten(pref_params).concat(
    [
      { param: "so_slope", val: so_slope},
      { param: "so_int", val: so_int}
    ]
  )
}
'
```

```{r}
# child_model_param<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, childModelParam , sep='\n'),
#   data = list(prefData = child_ex2_data, infData = child_ex1_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_model_param.rds")

child_model_param <- readRDS("../../stats/saves/child_model_param.rds")%>%
  select(value) %>%
  map_df(bind_rows)%>%
  group_by(param,condition)%>%
  summarise(param_map = estimate_mode(val))%>%
  mutate(cond = paste(param,condition, sep = "_"))%>%
  ungroup()%>%
  select(cond,param_map)%>%
  spread(cond,param_map)%>%
  rename(so_int = so_int_NA,
         so_slope = so_slope_NA)

```{r}
# visualize model priors in comparison to data 
child_prior_plot <- child_ex2_data %>%
  group_by(id,age_num,minage,condition)%>%
  summarise(correct = mean(correct))%>%
  mutate(model = ifelse(condition == "different_speaker",
                        plogis(child_model_param$pref_int_different_speaker + child_model_param$pref_slope_different_speaker * (age_num-minage)),
                        plogis(child_model_param$pref_int_same_speaker + child_model_param$pref_slope_same_speaker * (age_num-minage)
                        )))

ggplot(data = child_prior_plot, aes(x = age_num, y = correct, col = condition)) +
  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
  geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
  geom_line(aes(x = age_num, y = model, col = condition), size = 1.5, lty = 2)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_solarized(name = "Condition")+
  scale_fill_solarized(name = "Condition")
```

```{r}
# visualize speaker optimality in comparison to data 
child_so_plot <- child_ex1_data %>%
  group_by(id,age_num,minage)%>%
  summarise(correct = mean(correct))%>%
  mutate(model = child_model_param$so_int + child_model_param$so_slope * (age_num - minage))

ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
  geom_line(alpha = .5, size = .7)+
  labs(x="Age",y="Speaker optimality parameter")+
  theme_few() +
  geom_hline(yintercept = 0, lty=2)+
  ylim(-3,3)+
  guides(alpha = F)
```

```{r}
ex3_model_data <- child_ex3_data%>%
  mutate(so_int = child_model_param$so_int,
         so_slope = child_model_param$so_slope,
         pref_int_different_speaker = child_model_param$pref_int_different_speaker,
         pref_slope_different_speaker = child_model_param$pref_slope_different_speaker,
         pref_int_same_speaker = child_model_param$pref_int_same_speaker,
         pref_slope_same_speaker = child_model_param$pref_slope_same_speaker,
         so = so_int+so_slope*(age_num-min(age_num)),
         diff_prior = plogis(pref_int_different_speaker+pref_slope_different_speaker*(age_num-min(age_num))),
         same_prior = plogis(pref_int_same_speaker+pref_slope_same_speaker*(age_num-min(age_num))))%>%
  group_by(id,trial)%>%
        mutate(priorProbs = ifelse(speaker == "same_speaker" & alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
                                   ifelse(speaker == "different_speaker" & alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
                                          ifelse(speaker == "same_speaker" & alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
                                                 list(c(diff_prior,diff_prior,1-diff_prior))

                                   ))))%>%
  ungroup()%>%
  select(speaker,age_num,minage,alignment,so,priorProbs,correct_inf)

```
## Model predictions

### Pragmatic model

```{r}
child.ex3.rsa.predictions <-'

var allData = dataFromR.ex3data

  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})

  var output = map(function(row){

    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)

    observe(noisyModelPredictions, row.correct_inf)

    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]

}, allData)

 return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})

```{r}
# child_ex3_pragm_model<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
#   data =list(ex3data = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model.rds")

child_ex3_pragm_model <- readRDS("../../stats/saves/child_ex3_pragm_model.rds")

child_ex3_pragm_model_predictions <- child_ex3_pragm_model%>%
  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
  mutate(model="pragmatic")%>%
  group_by(model,age,speaker,alignment)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

child_ex3_pragm_model_noise <- child_ex3_pragm_model %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

### Prior only model

```{r}
child.ex3.prior.only.predictions <-'

var allData = dataFromR.ex3data

  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})

  var output = map(function(row){

    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, row.priorProbs,row.so)

      var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: row.priorProbs}));
      return obj.shape == "circle" ? 1 : 0
       }})

    observe(noisyModelPredictions, row.correct_inf)

    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]

}, allData)

 return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})

```{r}
# child_ex3_prior_only_model<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, child.ex3.prior.only.predictions , sep='\n'),
#   data =list(ex3data = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model.rds")

child_ex3_prior_only_model <- readRDS("../../stats/saves/child_ex3_prior_only_model.rds")

child_ex3_prior_only_model_predictions <- child_ex3_prior_only_model%>%
  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
  mutate(model="prior_only")%>%
  group_by(model,age,speaker,alignment)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

child_ex3_prior_only_model_noise <- child_ex3_prior_only_model %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

### Flat prior model

```{r}
child.ex3.flat.prior.predictions <-'

var allData = dataFromR.ex3data

  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})

  var output = map(function(row){

    var noise = logistic(noise_int + noise_slope * (row.age_num - row.minage))

    var prior = [.5, .5, .5]

    var modelPredictions = pragmaticListener({label: "dax", point: 2 }, prior,row.so)

    observe(noisyModelPredictions, row.correct_inf)

    return  [row.age_num + "/" + row.speaker + "/" + row.alignment, Math.exp(noisyModelPredictions.score(1))]

}, allData)

 return extend(_.fromPairs(output), {noise_int: noise_int, noise_slope: noise_slope})

```{r}
# child_ex3_flat_prior_model<- webppl(
#   program_code = paste(rsaUtils, childRsaModel, child.ex3.rsa.predictions , sep='\n'),
#   data =list(ex3data = ex3_model_data),
#   data_var = "dataFromR",
#   model_var = "model",
#   chains = 4,
#   cores = 4,
#   inference_opts = list(method = "MCMC", samples = 3000, burn = 1000, verbose = T)
# )%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model.rds")

child_ex3_flat_prior_model <- readRDS("../../stats/saves/child_ex3_flat_prior_model.rds")

child_ex3_flat_prior_model_predictions <- child_ex3_flat_prior_model%>%
  filter(!(Parameter %in% c("noise_int","noise_slope")))  %>%
  separate(Parameter, into = c("age","speaker", "alignment"), sep="/")%>%
  mutate(model="flat_prior")%>%
  group_by(model,age,speaker,alignment)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))%>%
  ungroup()%>%
  mutate(age = as.numeric(age))

child_ex3_flat_prior_model_noise <- child_ex3_flat_prior_model %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))

### Plot for noise parameter

```{r visualizing noise parameters}
plot_noise_param <- data_frame(
  age = rep(seq(0,2, by = 0.05),3),
  model = c(
    rep("pragmatic",41),
    rep("prior_only",41),
    rep("flat_prior",41)),
  int = c(
    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41),
    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_int")%>%pull(mean),41)
    ),
  slope = c(
    rep(child_ex3_pragm_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
    rep(child_ex3_prior_only_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41),
    rep(child_ex3_flat_prior_model_noise%>%filter(Parameter=="noise_slope")%>%pull(mean),41)
    )
) %>%
  mutate(y = plogis(int + slope *age))

plot_child_noise_param_dev <- ggplot(plot_noise_param, aes(x = age, y= y, col = model))+
  geom_line(size = 2)+
  ylim(0,1)+
  theme_few()+
  ylab("Noise parameter")+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

child_noise_param_by_model <- bind_rows(
  child_ex3_pragm_model%>%mutate(model="pragmatic"),
  child_ex3_prior_only_model%>%mutate(model="prior_only"),
  child_ex3_flat_prior_model%>%mutate(model="flat_prior")
) %>%
  filter(Parameter %in% c("noise_int", "noise_slope"))

plot_child_noise_param_by_model <- ggplot(child_noise_param_by_model, aes(x = value, col = model))+
  geom_density()+
  facet_grid(model~Parameter, scales = 'free')+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

ggarrange(plot_child_noise_param_by_model, plot_child_noise_param_dev, common.legend = T)
```

### Plot model predictions and data

```{r}
child_model_predictions <- bind_rows(
  child_ex3_pragm_model_predictions,
  child_ex3_flat_prior_model_predictions,
  child_ex3_prior_only_model_predictions
  )

plot_child_ex3_data <- child_ex3_data%>%
  group_by(age_num,speaker,alignment)%>%
  summarise(mean = mean(correct_inf))

ggplot(child_model_predictions)+
  #geom_jitter(data = plot_child_ex3_data, aes(x = age_num, y = mean), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = child_ex3_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "loess", span = 1.5,  se = T,  alpha = .5)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(speaker~alignment)+
  theme_few()+
  scale_color_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))+
  scale_fill_manual(name="Model",
                     breaks=c("pragmatic","flat_prior","prior_only"),
                     values= c("#859900","#6c71c4","#b58900"))

### Correlation plot model predictions and data

```{r}
child_cor_data <- child_ex3_data %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(speaker, alignment, age_bin) %>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         Data_ci_lower  = qbeta(.025, a, b),
         Data_ci_upper = qbeta(.975, a, b),
         Data = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

child_cor_model <- child_model_predictions %>%
  mutate(age = ifelse(age<4,"3","4"))%>%
  group_by(model,speaker,alignment, age)%>%
  summarise(Model = mean(mean),
            Model_ci_lower =hdi_lower(mean) ,
            Model_ci_upper = hdi_upper(mean))

child_cor_plot <- child_cor_model %>%
  ungroup()%>%
  mutate(Data = rep(child_cor_data$Data,3),
         Data_ci_lower = rep(child_cor_data$Data_ci_lower,3),
         Data_ci_upper  =rep( child_cor_data$Data_ci_upper,3))

ggplot(data = child_cor_plot,aes(x = Model, y = Data, col = age)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
  coord_fixed()+
  facet_grid(~model)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = Model, y = Data), inherit.aes = F)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few() + 
  scale_colour_ptol()
```

### 2019-03-08 stats/kids/kids_model_predictions.Rmd
advance model description for paper

```{r}
params_by_age<- readRDS("../saves/params_by_age.rds")

@@

ex3_data_param <- ex3_data%>%
  mutate(different_speaker_pref_int = model_params$different_speaker_pref_int,
         different_speaker_pref_slope = model_params$different_speaker_pref_slope,
         so_int = model_params$NA_so_int,
         so_slope = model_params$NA_so_slope,
         same_speaker_pref_int = model_params$same_speaker_pref_int,
         same_speaker_pref_slope = model_params$same_speaker_pref_slope,
         so = plogis(so_int+so_slope*(age_num-min(age_num))),
         diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
         same_prior = plogis(same_speaker_pref_int+same_speaker_pref_slope*(age_num-min(age_num))))%>%
  group_by(subid,trial)%>%
        mutate(priorProbs = ifelse(Speaker == "same_speaker" & Alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
                                   ifelse(Speaker == "different_speaker" & Alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
                                          ifelse(Speaker == "same_speaker" & Alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
                                                 list(c(diff_prior,diff_prior,1-diff_prior))

@@

  var noise_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var noise_int = uniformDrift({a: -2, b: 2, width: 0.4})

@@

```{r}
dev_noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, developmentalNoisyModelPred , sep='\n'),
  data =list(ex3data = ex3_data_param),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
)

@@

@@

ggplot(models)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()

>>>>

```{r}
params_by_age<- readRDS("../saves/child_model_param.rds")

@@

ex3_data_param <- ex3_data%>%
  mutate(different_speaker_pref_int = model_params$different_speaker_pref_int,
         different_speaker_pref_slope = model_params$different_speaker_pref_slope,
         so_int = model_params$NA_so_int,
         so_slope = model_params$NA_so_slope,
         same_speaker_pref_int = model_params$same_speaker_pref_int,
         same_speaker_pref_slope = model_params$same_speaker_pref_slope,
         so = so_int+so_slope*(age_num-min(age_num)),
         diff_prior = plogis(different_speaker_pref_int+different_speaker_pref_slope*(age_num-min(age_num))),
         same_prior = plogis(same_speaker_pref_int+same_speaker_pref_slope*(age_num-min(age_num))))%>%
  group_by(subid,trial)%>%
        mutate(priorProbs = ifelse(Speaker == "same_speaker" & Alignment == "congruent", list(c(1-same_prior,1-same_prior,same_prior)),
                                   ifelse(Speaker == "different_speaker" & Alignment == "congruent", list(c(1-diff_prior,1-diff_prior,diff_prior)),
                                          ifelse(Speaker == "same_speaker" & Alignment == "incongruent", list(c(same_prior,same_prior,1-same_prior)),
                                                 list(c(diff_prior,diff_prior,1-diff_prior))

@@

  var noise_slope = uniformDrift({a: -5, b: 5, width: 0.2})
  var noise_int = uniformDrift({a: -5, b: 5, width: 0.1})

@@

```{r}
dev_noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, developmentalNoisyModelPred , sep='\n'),
  data =list(ex3data = ex3_data_param),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 8000, burn = 2000, verbose = T)
)

@@

plot.posterior.noise <- posterior.noise%>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value))%>%
  spread(Parameter,mean)

x <- data_frame(
  age = rep(seq(0,2, by = 0.05),1),
  `int/slope` = c(rep(paste(round(plot.posterior.noise$noise_int,2),round(plot.posterior.noise$noise_slope,2), sep = "/"),41)),
  int = c(rep(plot.posterior.noise$noise_int,41)),
  slope = c(rep(plot.posterior.noise$noise_slope,41))
) %>%
  mutate(y = plogis(int + slope *age))

ggplot(x, aes(x = age, y= y,col = `int/slope`))+
  geom_line()+
  ylim(0,1)

@@

ggplot(models)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x = age, ymin = ci_lower, ymax = ci_upper, fill = model), alpha = .4) +
  geom_line(aes(x = age, y = mean, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_num, y = correct_inf), col = "black", method = "loess", span = 1, se = T,  alpha = .5, size = .4)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()
